---
title: 'Part 2: chi-square with lizard''s tails'
author: "Michelle Lepori-Bui"
date: "12/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(broom)
library(janitor)



```

```{r}
lizards <- read_csv(here("data","lizards.csv"))

```
Get counts of lizards by species

```{r}
lizards %>% 
  count(spp) %>% 
  arrange(-n)
```

## make a subset 

- utst lizards
- 3 highest trapped sites (IBPE enclosure grassland, RABB rabbit mesquite site, "EAST" east tarbrush site)
- tail condition is recorded (w whole, b broken)

unique (utst$site) check to see that filter worked 

```{r}
utst <- lizards %>% 
  filter (spp == "UTST") %>% 
  filter (site %in% c("IBPE", "RABB", "EAST")) %>% 
  filter(tail %in% c("B","W"))
```

## Find counts and proportions of lizards with broken or whole tails at each site

```{r}
utst %>% 
  count(site, tail)
```
```{r}
tail_counts <- utst %>% 
  janitor::tabyl(site,tail)

tail_proportions <- tail_counts %>% 
  janitor::adorn_percentages() %>% 
  janitor::adorn_pct_formatting(digits = 2) %>% 
  janitor::adorn_ns()
```


## convert to contingency table

use 'column_to_rowname()'

```{r}
lizard_ct <- tail_counts %>% 
  column_to_rownames(var = "site")
```

## chi-square

```{r}
lizard_x2 <- chisq.test(lizard_ct)

lizard_tidy <- broom::tidy(lizard_x2)
```

There is a significant asscociation (ie nonindependence) between site and lizard tail breakage ($\chi$^2^(`r lizard_tidy$parameter`) = `r lizard_tidy$statistic`, *p* = `r lizard_tidy$p.value`)

