---
title: "Part 1 Multiple Linear Regression"
author: "Michelle Lepori-Bui"
date: "12/5/2020"
output: html_document
---

```{r setup, message = FALSE, warning = FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(stargazer)
```

Colinearity - 
```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color=species))
```

## Build a few different models

body mass will be the dependent variable

```{r}
lm1 <- lm(body_mass_g ~ flipper_length_mm + species, data = penguins)

lm2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

lm3 <- lm(body_mass_g ~ flipper_length_mm + species + sex + bill_length_mm, data = penguins)

lm4 <- lm(body_mass_g ~ flipper_length_mm + species + sex + bill_length_mm + island, data = penguins)

```

the lower the AIC the better balance between complexity and accuracy

## Find the AIC value for each model

the lower the AIC the better balance between complexity and fit

```{r}
AIC(lm1)
AIC(lm2)
AIC(lm3) # lowest
AIC(lm4)
```

## use stargazer package for a table with multiple model outputs

```{r, results = 'asis'}
stargazer(lm1, lm3, lm4, type = "html")
```

## omitted variable bias

simpsons paradox - reverse of interpretation if you omit a variable

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = bill_depth_mm)) +
  geom_point() +
  geom_smooth(method = "lm")
```


```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, 
                            y = bill_depth_mm,
                            group = species)) +
  geom_point(aes(color = species)) +
  geom_smooth(method = "lm")
```

















